% Syed Saadat Ahmad — résumé
% Build:  tectonic SyedSaadatAhmad-Resume.tex   (or pdflatex)
\documentclass[10pt,letterpaper]{article}

\usepackage[top=0.4in,bottom=0.4in,left=0.5in,right=0.5in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}

\definecolor{linkblue}{HTML}{2563EB}
\hypersetup{
  colorlinks=true,
  urlcolor=linkblue,
  linkcolor=linkblue,
  pdftitle={Syed Saadat Ahmad — Resume},
  pdfauthor={Syed Saadat Ahmad}
}

\pagestyle{empty}
\setlength{\parindent}{0pt}

% Section headers: bold, slightly larger, full-width rule beneath
\titleformat{\section}{\large\bfseries}{}{0em}{}[\vspace{1pt}\titlerule]
\titlespacing{\section}{0pt}{4pt}{2pt}

% Tight bullet lists
\setlist[itemize]{leftmargin=1.4em, itemsep=0pt, topsep=1pt, parsep=0pt,
  label=\textbullet}

% Separator between role / company / location
\newcommand{\sep}{\,\textbullet\,}

% Entry header: bold role, company, italic location ... right-flushed italic date
\newcommand{\entry}[4]{%
  \textbf{#1}\sep #2\sep \textit{#3}\hfill\textit{#4}\par}

\begin{document}

% ── Header ──────────────────────────────────────────────────────────────
\begin{center}
  {\Huge Syed Saadat Ahmad}\\[3pt]
  {\small \href{mailto:s.saadat.ahmad@gmail.com}{s.saadat.ahmad@gmail.com}
   \ \ $|$\ \ +91 74510 77808 \ \ $|$\ \ Aligarh, India}
\end{center}

% ── Experience ──────────────────────────────────────────────────────────
\section*{Experience}
\addcontentsline{toc}{section}{Experience}

\entry{Software Engineer Intern}{Recklabs Services}{Remote}{May 2026 -- Present}
\begin{itemize}
  \item Building and shipping an MVP-stage, privacy-first desktop AI product --- a Model Context Protocol (MCP) platform that wires custom connectors into Claude Desktop --- owning the web, licensing, and distribution layers end to end.
  \item Built the marketing site and product portal as a server-rendered FastAPI + Jinja2 app on PostgreSQL (SQLAlchemy, Alembic), with JWT/bcrypt auth and a tamper-proof, compiled entitlement gate for licensing.
  \item Engineered on-demand installer builds: connectors selected at login are compiled per user into a custom Windows \texttt{.exe} via GitHub Actions runners (Inno Setup), with auth-gated delivery and automatic Claude Desktop wiring.
  \item Hardened distribution by compiling Python connectors to native binaries (\texttt{.pyd}/\texttt{.exe}) with Nuitka for tamper resistance, deployed via Docker Compose on a VPS behind Nginx.
\end{itemize}

\entry{Software Developer Intern}{Telecrm}{Aligarh, India}{Aug 2025 -- May 2026}
\begin{itemize}
  \item Worked in an Agile team on 14-day sprints, collaborating daily with QA and engineering to prioritise and ship automation improvements on schedule.
  \item Expanded automated E2E regression suites (Puppeteer, Jasmine, FFMPEG, Allure, AWS S3) and integrated them into the CI/CD pipeline.
  \item Operated and monitored test pipelines end-to-end, triaging failures, root-causing flakiness, and ensuring reliable execution across every release cycle.
  \item Upgraded reporting by integrating test-case history into Allure Reports, giving the team clear visibility into release-level trends and failure patterns.
\end{itemize}

\entry{Satellite Payload Designer}{SS AMU SAT}{Aligarh, India}{Jul 2024 -- Jan 2026}
\begin{itemize}
  \item Collaborated in an interdisciplinary team of 30+ members including faculty, industry engineers, and ISRO scientists to develop a university nanosatellite.
  \item Implemented and tested the imaging payload on a Raspberry Pi Compute Module 4, handling driver integration, image-capture pipeline, and on-board storage.
  \item Configured CAN bus communication between the payload and multiple satellite subsystems and sensors.
  \item Designed geolocation-driven automation to trigger satellite image acquisition based on orbital position.
\end{itemize}

\entry{Backend Web Developer Intern}{Orbitalink Pvt. Ltd.}{Aligarh, India}{May 2025 -- Jul 2025}
\begin{itemize}
  \item Designed and deployed a CI/CD pipeline using GitHub Actions with separate workflows for production and development environments.
  \item Built internal REST APIs covering user authentication, session management, role-based admin privileges, and third-party service integrations.
  \item Led the migration of the system from Flask + SQLite3 to Next.js + PostgreSQL, improving scalability and query performance.
\end{itemize}

% ── Projects ────────────────────────────────────────────────────────────
\section*{Projects}

\textbf{nCrypt} \ \href{https://saadatahmad.pythonanywhere.com}{\small View}
\begin{itemize}
  \item Flask-based web platform for creating, sharing, and applying custom encryption schemes; deployed on PythonAnywhere with end-to-end HTTPS.
  \item Engineered RESTful APIs, SQLite data models, and Werkzeug-powered password hashing for secure user and scheme management.
\end{itemize}
\vspace{3pt}

\textbf{JannSeva} \ \href{https://github.com/Saadat-Ahmad/JannSeva}{\small View}
\begin{itemize}
  \item AI-driven healthcare app designed for rural India, supporting 120+ regional dialects via integrated NLP.
  \item Incorporated weather and air-quality APIs to generate hyper-local, location-specific health insights.
  \item Implemented OTP-based authentication via Twilio, prioritising accessibility for low-tech and first-time smartphone users.
\end{itemize}

% ── Skills ──────────────────────────────────────────────────────────────
\section*{Skills}
\textbf{Languages:} Python, C, C++, JavaScript, TypeScript\\
\textbf{Frontend:} React, React Native, Next.js, Angular, HTML/CSS, Tailwind CSS\\
\textbf{Backend:} FastAPI, Flask, Django, Node.js, REST APIs\\
\textbf{Databases:} PostgreSQL, SQLite, MySQL, MongoDB\\
\textbf{DevOps:} Docker, Docker Compose, GitHub Actions, Bitbucket Pipelines, Nginx, VPS Deployments, CI/CD

% ── Education ───────────────────────────────────────────────────────────
\section*{Education}
\textbf{Bachelor of Technology in Computer Engineering}\hfill\textit{2027}\\
Z.H. College of Engineering and Technology, Aligarh Muslim University

\end{document}
